\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Benjamin A. Pusey}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    (781) 534-5448       \hfill Boston, MA 02118 \\
    \noindent bpusey@bu.edu  \hfill https://github.com/moneydance \vspace{0mm}\\\vspace{-4.5mm}
    
    \section{\mysidestyle Programming\\Experience}

    \textbf{Programming Languages:} Python, Java, JavaScript(ES5, ES6, TypeScript), C++, CSS3, Sass, HTML5, SQL $\vert$
 	\textbf{Frameworks:} AngularJS, Angular2+, Django, Flask, Spring, Express/Nest.js $\vert$
    \textbf{Misc:} Node, REST, Elasticsearch, OAuth, RxJS, Webpack, Gulp, OpenCV, Git, Docker

    \section{\mysidestyle Education}

    \textbf{Boston University}, Class of 2016 $\vert$ Boston, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{BA, Computer Science} \hfill GPA: 3.44/Major GPA: 3.77 \hfill \textbf{Sep 2013 -- May 2016}\\ Completed standard computer science classes in probability, linear algebra, data structures, and algorithms. High-level coursework included topics in queueing/scheduling, concurrency/synchronization, computer networking, software engineering, image/video computing, graph theory, and game theory.
    \section{\mysidestyle Professional\\Experience}

    \textbf{Fidelity Investments}, Boston, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Associate Software Engineer} \hfill \textbf{Sep 2016 -- present}\\
    Worked on internal fund management tools
	as a full stack software engineer, in an agile shop.
    \begin{itemize}
    \item Completed training in Fidelity's Leap program. Topics included Java, Spring, JavaScript, and SQL.
    \item Assisted in developing a gradual plan to break up our monolithic application.
	\item Helped transition greenfield front-end development to Angular 2+.
	\item Created a micro service for full text search on financial instruments with Elasticsearch. 
    \item Developed new RESTful endpoints in Spring.
    \end{itemize}

    \textbf{TJX}, Marlborough, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Advanced Threat Assessment Intern} \hfill \textbf{May 2015 -- Aug 2015}\\
    Worked on a small team to develop an internal web application that tracks and buckets new security threats.
    \begin{itemize}
    	\item Gathered requirements and developed iteratively to improve and add desired functionality.
    	\item Created frontend with AngularJS 1.4.
    	\item Developed RESTful API using Python Flask and MongoDB.
    	\item The app was packaged in Docker containers and hosted using Gunicorn and Nginx.
    \end{itemize}
    \textbf{Downtyme}, Boston, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Oct 2014 -- May 2015}\\
    Collaborated with a group of students to develop Downtyme, a location-based scheduling app that allowed you to make plans with nearby friends.
    \begin{itemize}
    	\item Worked with a team on the backend infrastructure. Created an API and SQL database using Python Django.
    	\item Built a mobile website so non-users could view and respond to plans.
    \end{itemize}
   \section{\mysidestyle Projects}
   \textbf{Tracking NBA Field Goals}, Boston University \vspace{2mm}\\\vspace{1mm}%
\vspace{-2mm}Worked with OpenCV to create an application that tracked basketball and player movement from NBA youtube clips. The application recorded made and missed shots.
    \section{\mysidestyle Honors And Awards}
    Winner of MIT Enterprise Forum’s Beantown Throwdown (Downtyme) \hfill \textbf{2014}\\
        Deans List \hfill \textbf{2013 -- 2016}\\

    

\end{resume}
\end{document}
